---
name: Kittipos
surname: Sirivongrungson
position: "Medical Doctor"
address: "Department of Physiology Faculty of Medicine Siriraj Hospital,\\tabularnewline Mahidol University"
phone: 085-199-1962
email: "kittipos.sir@mahidol.edu"
github: Lightbridge-KS
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
here::i_am("CV-KS-Hyndman/CV-KS-Hyndman.Rmd")
library(here)
library(readr)
library(vitae)
library(tibble)

source(here("R/latex_helper.R"))
```

```{r read_cv, include=FALSE}
cv <- read_rds(here("data/cv_raw.Rds"))
```

# Current Positions

```{r work}
cv$work %>% 
  detailed_entries(
    what = Title,
    with = Unit,
    when = glue::glue("{Start_yr} - {End_yr}")
  )
```

# Educations

```{r edu}
cv$edu %>% 
  mutate(Details = latex_color(Details, "gray", .na = "")) %>% 
  detailed_entries(what = Degree,
                   when = glue::glue("{Start_yr} - {End_yr}"),
                   with = Institution,
                   where = Details,
                   .protect = FALSE
                   )
```

# Medical Competency Assessment

```{r nl2}
cv$nl2 %>% 
  detailed_entries(
    what = Step,
    when = Yr,
    why = Text
  )
```

# Academic Trainings

```{r eval=FALSE}
cv$acad %>% 
  mutate(link = latex_hyperlink("Link", Certificate),
         link = paste0("--- Certificate: ", link))
```

```{r acad}
cv$acad[1:3, ] %>% 
  mutate(link = latex_hyperlink("Link", Certificate, color = "purple"),
         prefix_link = latex_color("--- Certificate: ", color = "gray"),
         full_link = paste0(prefix_link, link)
         ) %>% 
  detailed_entries(
    what = Title,
    with = By,
    where = full_link,
    when = Yr,
    .protect = F
  )
```

```{r}
cv$acad[4, ] %>% 
  detailed_entries(
    what = Title,
    with = By,
    when = Yr,
    .protect = T
  )
```

# Other Conferences & Trainings

```{r}
cv$otherTr %>% 
  mutate(prefix_link = latex_color("--- Certificate: ", color = "gray")) %>% 
  mutate(link = latex_hyperlink("Link", Certificate, color = "purple"),
         full_link = paste0(prefix_link, link)
         ) %>% 
  mutate(
    By = latex_hyperlink(By, By_link, color = "black")
    ) %>% 
  detailed_entries(
    what = Title,
    with = By,
    where = full_link,
    when = Yr,
    .protect = F
    )
```

# Elective Activities

```{r}
cv$elective %>% 
  detailed_entries(
    what = Title,
    with = Where,
    when = Yr
  )
```

# Research Experience

```{r}
cv$research %>% 
  detailed_entries(
    what = Title,
    with = glue::glue("With: {With}"),
    when = Status
  )
```

# Projects --- Web applications

\hfill\break

|        During my internship at the Physiology Department, I have developed various web applications in order to automate tasks and improve workflows that belong to these categories:

\hfill\break

### E-learning systems:

```{r app, include=FALSE}
app_latex <- cv$app %>% 
  mutate(text = latex_hyperlink(latex_bold(Name), Link, color = "purple")) %>% 
  dplyr::pull(text)

cv$app
```


-   `r app_latex[1]`

    -   This web application performs MCQ item analysis of student's quiz report from [SELECx](http://selecx.si.mahidol.ac.th).

-   `r app_latex[2]`

    -   This web application combines score and checks student's submission from [SELECx](http://selecx.si.mahidol.ac.th).

### Physiology Educations:

-   `r app_latex[3]`

    -   This web application converts lung volumn from [ATPS](https://medical-dictionary.thefreedictionary.com/ambient+temperature+and+pressure%2C+saturated) to [BTPS](https://medical-dictionary.thefreedictionary.com/body+temperature+and+pressure%2c+saturated).

-   `r app_latex[4]`

    -   This web application predicts metabolic rate and oxygen consumption from Harvard's spirometer tracing as used in exercise studies laboratory class.

### Research:

-   `r app_latex[5]`

    -   This web application combines LabChart's HRV Report files from `.txt` to single Excel table for further data analysis.

\hfill\break

# Skills

\hfill\break

## R-programming for Data Science:

-   **Exploratory Data Analysis** using [\textcolor{purple}{tidyverse packages}](https://www.tidyverse.org)

-   **Inferential Statistics** using [\textcolor{purple}{rstatix package}](https://rpkgs.datanovia.com/rstatix/)

-   **Supervised Learning** using Linear Regression, Spline and Logistic Regression

-   **Unsupervised Learning** using Principal Component Analysis

-   **Web application** using [\textcolor{purple}{shiny package}](https://shiny.rstudio.com)

-   **Programming Environment** using [\textcolor{purple}{RStudio}](https://www.rstudio.com) and [\textcolor{purple}{R Markdown}](https://rmarkdown.rstudio.com)


## Other Technical Skills:

-   Basic Python and Jupyter Notebook
-   Google App Script
-   Unix command line
-   Google Sheets and Microsoft Excel

\vfill


```{r footer, include=FALSE}
### Create a Footer and Place in \rfoot{}
footer <- paste0(
  latex_color("Source code of this document can be found in ", "gray"),
  latex_hyperlink("Github",
    "https://github.com/Lightbridge-KS/CV",
    color = "purple"
  )
)

footer
```

\rfoot{`r footer`}



