---
name: Kittipos
surname: Sirivongrungson
position: "Medical Doctor"
address: "Department of Physiology Faculty of Medicine Siriraj Hospital,\\tabularnewline Mahidol University"
phone: 085-199-1962
email: "kittipos.sir@mahidol.edu"
github: Lightbridge-KS
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
here::i_am("CV-KS-Hyndman/CV-KS-Hyndman.Rmd")
library(here)
library(readr)
library(vitae)
library(tibble)

source(here("R/latex_helper.R"))
```

```{r read_cv, include=FALSE}
cv <- read_rds(here("data/cv.Rds"))
```

# Employments

```{r work}
cv$work %>% 
  detailed_entries(
    what = Title,
    with = Unit,
    when = glue::glue("{Start_yr} - {End_yr}")
  )
```

# Educations

```{r edu}
cv$edu %>% 
  detailed_entries(what = Degree,
                   when = glue::glue("{Start_yr} - {End_yr}"),
                   with = Institution,
                   )
```

# Medical Competency Assessment

```{r nl2}
cv$nl2 %>% 
  detailed_entries(
    what = Step,
    when = Yr,
    why = Text
  )
```

# Academic Trainings

```{r eval=FALSE}
cv$acad %>% 
  mutate(link = latex_hyperlink("Link", Certificate),
         link = paste0("--- Certificate: ", link))
```

```{r acad}
cv$acad[1:3, ] %>% 
  mutate(link = latex_hyperlink("Link", Certificate, color = "purple"),
         prefix_link = latex_color("--- Certificate: ", color = "gray"),
         full_link = paste0(prefix_link, link)
         ) %>% 
  detailed_entries(
    what = Title,
    with = By,
    where = full_link,
    when = Yr,
    .protect = F
  )
```

```{r}
cv$acad[4, ] %>% 
  detailed_entries(
    what = Title,
    with = By,
    when = Yr,
    .protect = T
  )
```

# Other Conferences & Trainings

```{r}
cv$otherTr %>% 
  mutate(link = latex_hyperlink("Link", Certificate, color = "purple"),
         prefix_link = latex_color("--- Certificate: ", color = "gray"),
         full_link = paste0(prefix_link, link)
         ) %>% 
  detailed_entries(
    what = Title,
    with = By,
    where = full_link,
    when = Yr,
    .protect = F
    )
```

# Research Experience

```{r}
cv$research %>% 
  detailed_entries(
    what = Title,
    with = glue::glue("With: {With}"),
    when = Status
  )
```

# Projects --- Web applications

### E-learning systems

-   [\textcolor{purple}{\textbf{SELECx MCQ Analysis}}](https://si-physio-intern.shinyapps.io/SELECx_mcq_analysis/)

    -   This web application performs MCQ item analysis of student's quiz report from [SELECx](http://selecx.si.mahidol.ac.th).

-   [\textcolor{purple}{\textbf{SELECx Combine Quiz}}](https://si-physio-intern.shinyapps.io/SELECx_combine_quiz/)

    -   This web application combines score and checks student's submission from [SELECx](http://selecx.si.mahidol.ac.th).

### Physiology Educations

-   [\textcolor{purple}{\textbf{BTPS calculator}}](https://btps-calc.herokuapp.com)

    -   This web application converts lung volumn from [ATPS](https://medical-dictionary.thefreedictionary.com/ambient+temperature+and+pressure%2C+saturated) to [BTPS](https://medical-dictionary.thefreedictionary.com/body+temperature+and+pressure%2c+saturated).

-   [\textcolor{purple}{\textbf{Metabolic rate and Oxygen consumption calculator}}](https://metabolic-rate-calc.herokuapp.com)

    -   This web application predicts metabolic rate and oxygen consumption from Harvard's spirometer tracing as used in exercise studies laboratory class.

### Research

-   [\textcolor{purple}{\textbf{Combine HRV and BRS Report file}}](https://sips-ans.shinyapps.io/read_HRV_report)

    -   This web application combines LabChart's HRV Report files from `.txt` to single Excel table for further data analysis.
    
# Elective Activities


